---
title: "Generating realistic data with known truth using the `jointseg` package"
author: "M. Pierre-Jean, G. Rigaill, P. Neuvial"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
bibliography: jointseg.bib
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{PSSeg}
---

```{r, include=FALSE}
library("knitr")
opts_chunk$set(dev='png', fig.width=5, fig.height=5)
opts_knit$set(eval.after = "fig.cap")
```

This vignette illustrates how the `jointseg` package may be used to generate a variety of copy-number profiles from the same biological ``truth''.  Such profiles have been used to compare the performance of segmentation methods in @pierre-jean15performance

## Citing `jointseg`

```{r}
citation("jointseg")
```

## Setup

```{r, include=FALSE}
library("jointseg")
```

The parameters are defined as follows:
```{r}
n <- 1e4                                 ## signal length
bkp <- c(2334, 6121)                     ## breakpoint positions
regions <- c("(1,1)", "(1,2)", "(0,2)")  ## copy number regions
```

```{r}
ylims <- cbind(c(0, 5), c(-0.1, 1.1))
colG <- rep("#88888855", n)
hetCol <- "#00000088"
```

For convenience we define a custom plot function for this vignette:
```{r}
plotFUN <- function(dataSet, tumorFraction) {
    regDat <- acnr::loadCnRegionData(dataSet=dataSet, tumorFraction=tumorFraction)
    sim <- getCopyNumberDataByResampling(n, bkp=bkp,
                                         regions=regions, regData=regDat)
    dat <- sim$profile
    wHet <- which(dat$genotype==1/2)
    colGG <- colG
    colGG[wHet] <- hetCol
    plotSeg(dat, sim$bkp, col=colGG)
}
```


## Affymetrix data

```{r}
ds <- "GSE29172"
```

```{r, fig.cap=paste("Data set", ds, ":", pct, "% tumor cells")}
pct <- 1
plotFUN(ds, pct)
```

```{r, fig.cap=paste("Data set", ds, ":", pct, "% tumor cells (another resampling)")}
plotFUN(ds, pct)
```

```{r, fig.cap=paste("Data set", ds, ":", pct, "% tumor cells")}
pct <- 0.7
plotFUN(ds, pct)
```

```{r, fig.cap=paste("Data set", ds, ":", pct, "% tumor cells")}
pct <- 0.5
plotFUN(ds, pct)
```

## Illumina data

```{r}
ds <- "GSE11976"
```


## Session information
```{r}
sessionInfo()
```


## References
